---
title: "Assignment 1"
output:
  html_document: default
  word_document: default
  pdf_document: default
date: "2023-04-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#{css, echo=FALSE}
#P {
#  font-size: 32px;
#}


```{css}
.columns {display: flex;}
h1 {
  color: red;
  background-color: beige;
  font-size: 4.5em}
h2 {
  color: orange;
  background-color: brown;
  font-size: 2.5em}
p {color: green;}
````


# Assignment 1

## 1. Assign the value of five to a variable called a and the value of two to a variable called b.

```{r}
a <- 5
b <- 2
```


## 2. Compute the sum, difference, product and ratio of a and b (a always in the first place) and store the results to four different variables called r1, r2, r3, and r4

```{r}
r1 <- a + b
r2 <- a - b
r3 <- a * b
r4 <- a / b
```

## 3. Create a vector v1 which contains the values stored within the four variables from step 2

```{r}
v1 <- c(r1, r2, r3, r4)
```

## 4. Add a fifth entry to vector v1 which represents a by the power of b (i.e. a**b).

```{r}
r5 <- a ^ b
v1 <- c(r1, r2, r3, r4, r5)

```
## 5. Show the content of vector v1 (e.g. use the print function or just type the variable name in a separate row).

```{r}
print(v1)
v1
```
## 6. Create a second vector v2 which contains information on the type of mathematical operation used to derive the five results. Hence this vector should have five entries of values sum, difference,…

```{r}
v2 <- c("sum", "difference", "product", "ratio", "exponentiation")
```

## 7. Show the content of vector v2.
```{r}
v2
```

## 8. Combine the two vectors v1 and v2 into a data frame called df. Each vector should become one column of the data frame so you will end up with a data frame having 5 rows and 2 columns.

```{r}
df <- data.frame(v1, v2)
```

## 9. Make sure that the column with the data of v1 is named Results and v2 is named Operation.

```{r}
df <- data.frame(Results = v1, Operation = v2)
```

## 10. Show the entire content of df.

```{r}
df
```

## 11. Show just the entry of the cell in the second row and first column.
```{r}
df[2,1]

```



